The Development of a Collaborative Tool to Teach Debugging

### 2020-11-18 paper/paper.tex
paper changes

Debuggers exist at an intersection of tools and skills similar to
programming languages themselves. By becoming familiar with a specific
debugger, students learn techniques and paradigms necessary to use all
debuggers effectively.

@@

\subsubsection{Mozilla's rr}

@@

\subsubsection{Kubernetes and Docker}

TODO: Write about k8s and docker.

\subsubsection{React}

TODO: Write about react.

\subsubsection{Xterm.js}

TODO: Write about Xterm.js if I end up using it (which seems
overwhelmingly likely ATM).

>>>>

Debuggers exist at an intersection of tools and skills similar to
programming languages themselves. By becoming familiar with a specific
debugger, students learn techniques and paradigms necessary to use all
debuggers effectively.
\pagebreak

@@

\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt
\tikzset{every picture/.style={baselineskip=1pt}}
\tikzset{every picture/.style={/utils/exec={\ttfamily}}}

\begin{figure}[h!]
  \begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
    % uncomment if require: \path (0,494); %set diagram left start at 0, and has height of 494

    % Straight Lines [id:da7736831842096191] 
    \draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]    (380,110) -- (400,110) ;
    % Shape: Rectangle [id:dp04619309000609384] 
    \draw  [color={rgb, 255:red, 136; green, 136; blue, 136 }  ,draw opacity=1 ][fill={rgb, 255:red, 136; green, 136; blue, 136 }  ,fill opacity=1 ] (420,174) .. controls (420,171.79) and (421.79,170) .. (424,170) -- (546,170) .. controls (548.21,170) and (550,171.79) .. (550,174) -- (550,236) .. controls (550,238.21) and (548.21,240) .. (546,240) -- (424,240) .. controls (421.79,240) and (420,238.21) .. (420,236) -- cycle ;
    % Shape: Rectangle [id:dp1228490870487785] 
    \draw   (410,74) .. controls (410,71.79) and (411.79,70) .. (414,70) -- (536,70) .. controls (538.21,70) and (540,71.79) .. (540,74) -- (540,156) .. controls (540,158.21) and (538.21,160) .. (536,160) -- (414,160) .. controls (411.79,160) and (410,158.21) .. (410,156) -- cycle ;
    % Shape: Rectangle [id:dp17147478083974088] 
    \draw  [color={rgb, 255:red, 0; green, 0; blue, 0 }  ,draw opacity=1 ][fill={rgb, 255:red, 0; green, 0; blue, 0 }  ,fill opacity=1 ] (410,74) .. controls (410,71.79) and (411.79,70) .. (414,70) -- (536,70) .. controls (538.21,70) and (540,71.79) .. (540,74) -- (540,136) .. controls (540,138.21) and (538.21,140) .. (536,140) -- (414,140) .. controls (411.79,140) and (410,138.21) .. (410,136) -- cycle ;
    % Shape: Rectangle [id:dp08735176678895862] 
    \draw   (410,184) .. controls (410,181.79) and (411.79,180) .. (414,180) -- (536,180) .. controls (538.21,180) and (540,181.79) .. (540,184) -- (540,266) .. controls (540,268.21) and (538.21,270) .. (536,270) -- (414,270) .. controls (411.79,270) and (410,268.21) .. (410,266) -- cycle ;
    % Shape: Rectangle [id:dp9595297060154465] 
    \draw  [color={rgb, 255:red, 0; green, 0; blue, 0 }  ,draw opacity=1 ][fill={rgb, 255:red, 0; green, 0; blue, 0 }  ,fill opacity=1 ] (410,184) .. controls (410,181.79) and (411.79,180) .. (414,180) -- (536,180) .. controls (538.21,180) and (540,181.79) .. (540,184) -- (540,246) .. controls (540,248.21) and (538.21,250) .. (536,250) -- (414,250) .. controls (411.79,250) and (410,248.21) .. (410,246) -- cycle ;
    % Shape: Rectangle [id:dp8231056072369544] 
    \draw   (410,294) .. controls (410,291.79) and (411.79,290) .. (414,290) -- (536,290) .. controls (538.21,290) and (540,291.79) .. (540,294) -- (540,376) .. controls (540,378.21) and (538.21,380) .. (536,380) -- (414,380) .. controls (411.79,380) and (410,378.21) .. (410,376) -- cycle ;
    % Shape: Rectangle [id:dp6367028620504607] 
    \draw  [color={rgb, 255:red, 0; green, 0; blue, 0 }  ,draw opacity=1 ][fill={rgb, 255:red, 0; green, 0; blue, 0 }  ,fill opacity=1 ] (410,294) .. controls (410,291.79) and (411.79,290) .. (414,290) -- (536,290) .. controls (538.21,290) and (540,291.79) .. (540,294) -- (540,356) .. controls (540,358.21) and (538.21,360) .. (536,360) -- (414,360) .. controls (411.79,360) and (410,358.21) .. (410,356) -- cycle ;
    % Shape: Rectangle [id:dp8426243961763082] 
    \draw  [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]  (40,74) .. controls (40,71.79) and (41.79,70) .. (44,70) -- (106,70) .. controls (108.21,70) and (110,71.79) .. (110,74) -- (110,106) .. controls (110,108.21) and (108.21,110) .. (106,110) -- (44,110) .. controls (41.79,110) and (40,108.21) .. (40,106) -- cycle ;
    % Shape: Rectangle [id:dp3822373593536188] 
    \draw  [color={rgb, 255:red, 208; green, 2; blue, 27 }  ,draw opacity=1 ][line width=1.5]  (40,134) .. controls (40,131.79) and (41.79,130) .. (44,130) -- (106,130) .. controls (108.21,130) and (110,131.79) .. (110,134) -- (110,166) .. controls (110,168.21) and (108.21,170) .. (106,170) -- (44,170) .. controls (41.79,170) and (40,168.21) .. (40,166) -- cycle ;
    % Straight Lines [id:da30880840083209404] 
    \draw [color={rgb, 255:red, 208; green, 2; blue, 27 }  ,draw opacity=1 ][line width=1.5]    (120,150) -- (210,150) ;
    % Shape: Rectangle [id:dp5669106087613988] 
    \draw  [line width=1.5]  (220,74) .. controls (220,71.79) and (221.79,70) .. (224,70) -- (366,70) .. controls (368.21,70) and (370,71.79) .. (370,74) -- (370,166) .. controls (370,168.21) and (368.21,170) .. (366,170) -- (224,170) .. controls (221.79,170) and (220,168.21) .. (220,166) -- cycle ;
    % Straight Lines [id:da24300582818436978] 
    \draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]    (120,90) -- (152.5,90) -- (210,90) ;
    % Straight Lines [id:da9215040164115669] 
    \draw [color={rgb, 255:red, 208; green, 2; blue, 27 }  ,draw opacity=1 ][line width=1.5]    (380,130) -- (400,130) ;
    % Shape: Rectangle [id:dp3848745776815077] 
    \draw  [color={rgb, 255:red, 126; green, 211; blue, 33 }  ,draw opacity=1 ][line width=1.5]  (40,224) .. controls (40,221.79) and (41.79,220) .. (44,220) -- (176,220) .. controls (178.21,220) and (180,221.79) .. (180,224) -- (180,286) .. controls (180,288.21) and (178.21,290) .. (176,290) -- (44,290) .. controls (41.79,290) and (40,288.21) .. (40,286) -- cycle ;
    % Shape: Rectangle [id:dp9909839356430334] 
    \draw  [line width=1.5]  (220,224) .. controls (220,221.79) and (221.79,220) .. (224,220) -- (366,220) .. controls (368.21,220) and (370,221.79) .. (370,224) -- (370,286) .. controls (370,288.21) and (368.21,290) .. (366,290) -- (224,290) .. controls (221.79,290) and (220,288.21) .. (220,286) -- cycle ;
    % Straight Lines [id:da7242957436529691] 
    \draw [color={rgb, 255:red, 126; green, 211; blue, 33 }  ,draw opacity=1 ][line width=1.5]    (190.5,250) -- (200,250) -- (210.5,250) ;
    % Straight Lines [id:da6155515815274885] 
    \draw [color={rgb, 255:red, 126; green, 211; blue, 33 }  ,draw opacity=1 ][line width=1.5]    (10,220) -- (10,290) -- (10,270) -- (30,270) ;
    % Shape: Rectangle [id:dp04289765101859899] 
    \draw  [line width=1.5]  (40,344) .. controls (40,341.79) and (41.79,340) .. (44,340) -- (176,340) .. controls (178.21,340) and (180,341.79) .. (180,344) -- (180,386) .. controls (180,388.21) and (178.21,390) .. (176,390) -- (44,390) .. controls (41.79,390) and (40,388.21) .. (40,386) -- cycle ;
    % Straight Lines [id:da912738070320213] 
    \draw [line width=1.5]  [dash pattern={on 1.69pt off 2.76pt}]  (0,300) -- (0,400) -- (560,400) -- (560,30) -- (390,30) -- (390,180) -- (0,180) -- (0,300) -- (290,300) -- (390,300) -- (390,400) ;
    % Straight Lines [id:da9646857023949835] 
    \draw [line width=1.5]  [dash pattern={on 1.69pt off 2.76pt}]  (390,180) -- (390,330) ;
    % Straight Lines [id:da36286215804614264] 
    \draw [line width=1.5]  [dash pattern={on 1.69pt off 2.76pt}]  (0,180) -- (0,30) -- (390,30) ;
    % Straight Lines [id:da5365951688341024] 
    \draw [color={rgb, 255:red, 126; green, 211; blue, 33 }  ,draw opacity=1 ][line width=1.5]    (10,340) -- (10,370) -- (30,370) ;
    % Straight Lines [id:da2808441683655002] 
    \draw [color={rgb, 255:red, 126; green, 211; blue, 33 }  ,draw opacity=1 ][line width=1.5]    (10,170) -- (10,120) -- (30,120) ;

    % Text Node
    \draw (411,141) node [anchor=north west][inner sep=0.75pt]   [align=left] {User A};
    % Text Node
    \draw (412,73) node [anchor=north west][inner sep=0.75pt]   [align=left] {\textcolor[rgb]{1,1,1}{>}};
    % Text Node
    \draw (411,251) node [anchor=north west][inner sep=0.75pt]   [align=left] {User B};
    % Text Node
    \draw (412,183) node [anchor=north west][inner sep=0.75pt]   [align=left] {\textcolor[rgb]{1,1,1}{>}};
    % Text Node
    \draw (411,361) node [anchor=north west][inner sep=0.75pt]   [align=left] {User C};
    % Text Node
    \draw (412,293) node [anchor=north west][inner sep=0.75pt]   [align=left] {\textcolor[rgb]{1,1,1}{>}};
    % Text Node
    \draw (51,82) node [anchor=north west][inner sep=0.75pt]   [align=left] {\begin{minipage}[lt]{31.110000000000003pt}\setlength\topsep{0pt}
        \begin{center}
          12345
        \end{center}

      \end{minipage}};
    % Text Node
    \draw (401,42) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\large Users}};
    % Text Node
    \draw (11,42) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\large Debug Pods}};
    % Text Node
    \draw (51,142) node [anchor=north west][inner sep=0.75pt]   [align=left] {\begin{minipage}[lt]{31.110000000000003pt}\setlength\topsep{0pt}
        \begin{center}
          67890
        \end{center}

      \end{minipage}};
    % Text Node
    \draw (222,73) node [anchor=north west][inner sep=0.75pt]   [align=left] {Pod Communication\\Server};
    % Text Node
    \draw (11,192) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\large Pod \& User Control}};
    % Text Node
    \draw (42,223) node [anchor=north west][inner sep=0.75pt]   [align=left] {API Server\\Pod Management\\User Management};
    % Text Node
    \draw (222,223) node [anchor=north west][inner sep=0.75pt]   [align=left] {Frontend Server};
    % Text Node
    \draw (11,312) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\large Database}};
    % Text Node
    \draw (42,343) node [anchor=north west][inner sep=0.75pt]   [align=left] {User Storage\\Pod Storage};
    % Text Node
    \draw (1,2) node [anchor=north west][inner sep=0.75pt]   [align=left] {\begin{minipage}[lt]{12.931356000000001pt}\setlength\topsep{0pt}
        \begin{flushright}
          {\large 2.}
        \end{flushright}

      \end{minipage}};
    % Text Node
    \draw (362,37) node [anchor=north west][inner sep=0.75pt]   [align=left] {\begin{minipage}[lt]{12.931356000000001pt}\setlength\topsep{0pt}
        \begin{flushright}
          {\large a.}
        \end{flushright}

      \end{minipage}};
    % Text Node
    \draw (391,2) node [anchor=north west][inner sep=0.75pt]   [align=left] {\begin{minipage}[lt]{12.931356000000001pt}\setlength\topsep{0pt}
        \begin{flushright}
          {\large 1.}
        \end{flushright}

      \end{minipage}};
    % Text Node
    \draw (362,187) node [anchor=north west][inner sep=0.75pt]   [align=left] {\begin{minipage}[lt]{12.931356000000001pt}\setlength\topsep{0pt}
        \begin{flushright}
          {\large b.}
        \end{flushright}

      \end{minipage}};
    % Text Node
    \draw (363,307) node [anchor=north west][inner sep=0.75pt]   [align=left] {\begin{minipage}[lt]{12.24pt}\setlength\topsep{0pt}
        \begin{flushright}
          {\large c.}
        \end{flushright}

      \end{minipage}};

  \end{tikzpicture}

  \caption{Overview of the Collaborative Debugger}
  \label{debugger:overview}
\end{figure}

The next sections give an overview of the various tools used to create
the collaborative debugger.  The debugger consists of:

\begin{enumerate}
\item A frontend web app built using React that presents a debugging
  interface to the end user (\ref{react}).
\item A distributed backend managed by Kubernetes (\ref{k8s}), split into three parts:
  \begin{enumerate}
  \item A pod for each debugging instance which runs the rr debugger
    (\ref{rr}).  These communicate directly with users through
    websockets (\ref{socketio}).
  \item Pods running a frontend server written in Node which works in
    tandem with an API server created using Flask (\ref{flask/node}).
    The API server manages creation and destruction of debug sessions,
    as well as authentication.
  \item A MongoDB database.
  \end{enumerate}
\end{enumerate}

\subsubsection{Kubernetes}\label{k8s}

\subsubsection{Mozilla's rr}\label{rr}

@@

\subsubsection{socket.io}\label{socketio}

\subsubsection{Flask and Node}\label{flask/node}

\subsubsection{React and Xterm.js}\label{react}
